Contracts for unions and intersections are hard for Nickel

### 2021-05-03 paper.tex
Starting section on comparison, outlines

>>>>

\section{Current (Real life) implementations}

\info{The goal of this section is to outline existing languages that implement
union and intersection, in some form, and shortly compare these
with the semantics tried to obtain on research (WMW, KT)}

Unions and intersection are starting to become more and more common
on non-academic programming languages, as stated on the introduction,
unions are a natural abstraction for dynamic languages, where the type
of an expression could have many different shapes, without necessarily
having a mark to distinguish between them.
With this in mind, a valid question is how do these languages solve the
union/intersection conundrum? Or, even better, what is it that they
solve?

In the rest of this section we revisit some different approaches.

\subsection{Racket}

Racket is language based on Scheme mainly thought as a language to experiment
with different language desings and ideas. It provides a very complete contract
system.

Among those contracts, they provide \texttt{and/c} and \texttt{or/c} contracts.
These contracts are lightweight versions of unions and intersections, they simply
check that every contract holds, in the case of and/c, and that at least one contract
holds, in the case of or/c.

So, for instance, the usual usecase of intersection to encode overloading
does not work on Racket. Take a look at the next example, the function
\texttt{overload} shoudl accept a call like \texttt{(overload 3)}, but it fails
since it 3 is not a valid \texttt{string?}.

\texttt{(define/contract overload
(and/c (-> number? number?)
       (-> string? string?))
(λ (x) x))}

Even worst, the or/c contract doesn't allow to have multiple higher order
contracts that could (potentially) apply to a function, these have to be
differentiated by first order markers (for instance, the number of arguments).

\subsubsection*{case->}

Racket does provide an alternative for overloading methods, called the
\texttt{case->} contract, however, this overloading of methods only
works over contracts of functions with different amount of parameters.

\todo{Coming back to the problems of composing U/I with other typing
features, Racket has made a clear choice and decided that higher order
is more important (a wise decision)}

\subsection{Python - MyPy}
